Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-12-02 paper/reply.tex
Benchmarks

\begin{quote}
\textcolor{blue}{\textbf{Response:} 
We consider this extension for future work.}
\end{quote}

Some specific comments:

1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.

@@

3) I believe equation (10) does not correspond to the system on Figure 1. Please check. If needed, correct (11), (12) and (13) and the rest of the paper accordingly.
\begin{quote}
\textcolor{blue}{\textbf{Response:}
In fact, these equations are wrong. They have to be substituted by the following equations (1)-(5). This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
%%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
\end{equation}
%
\begin{equation}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
\end{equation}
%
\begin{equation}
H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} In section 3.3 we explain that there are two Fixed point domains in the control synthesis problem. Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual domain of the controller, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser which is used to try and synthesise a real plant. In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis. \textcolor{red}{This is an optimization of the tool and does not relate to the problem statement.} The reason for the 8-bit steps is because the tool uses byte alignment.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} The benchmarks used are from existing work on verification. There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons. }
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We only state the winning back-end in the
results table, annotating where the one-stage engine was faster. The two order
of magnitudes were measured empirically, since the one-stage engine times out
on the majority of benchmarks.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We did include an upper bound for both the
bit width and execution time. Given an arbitrarily high precision and given
unlimited execution time, the engine will always succeed.}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Cristina).}
\end{quote}

Some specific comments:
1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.

@@

3) I believe equation (10) does not correspond to the system on Figure 1. Please check. If needed, correct (11), (12) and (13) and the rest of the paper accordingly.
\begin{quote}
\textcolor{blue}{\textbf{Response:}
In fact, these equations are wrong. They have to be substituted by the following equations (1)-(5). This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
%%
%\begin{equation}
%\hat{Y}(z)=\nu_{1}(z)+Y(z)
%\end{equation}
%%
%\begin{equation}
%Y(z)=\hat{G}(z)\cdot(U(z)+\nu_{2}(z))
%\end{equation}
%%
%\begin{equation}
%U(z)=C(z)\cdot e(z)=C(z)\cdot (R(z)-\hat{Y}(z))
%\end{equation}
%%
%$$
%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot [\hat{C}(z)\cdot(R(z)-\hat{Y}(z))+\nu_{2}(z)]
%$$
%%
\begin{equation}
\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
\end{equation}
%
\begin{equation}
\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
\end{equation}
%
\begin{equation}
H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
\begin{equation}
H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
\end{equation}
}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
\end{quote}
